Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-06 analysis/TAS_memo/memo_TAS_reviewers.Rmd

@@

We have revised this discussion to remove such confusion.  The choice of the credible interval is a decision about how conservative one wishes to be about inferring bias from past strike data alone. We define bias "detection" narrowly to mean when $b = 0$ falls outside the chosen credible interval. Thus, the larger the credible interval, the greater the chance that zero falls within it. For the sake of clarity, we now focus on one credible interval (95%) in the paper and have placed simulation results based on other credible intervals in the Appendix. This does not necessarily fix the type I error, because this coverage probability refers to the true bias parameter (that is fixed in our simulations), and we are interested in "bias detection", i.e. whether the credible interval includes 0 or not. We also present sensitivity analysis for the selection of the nominal HPD level.

@@

>2. About the results presented in Figure 1 of Section 2.3, if we ignore the assumption of compatibility between historical and current data, in the cases of $\alpha$ = 0:5 and $\alpha$ = 1, does the bottom right corner in each panel indicate that the bias detection rate can be as high as 100% even when the true current bias is 0? If so, the Type I error seems to be very high in some cases. Similarly, the power (bias detection rate) seems low at the top left corner in each panel where bias is low in historical data but high in current data.

@@

@@

[INSERT] Will get Eric to check this (still no response from Xiaomeng)

@@

>>>>

While it is true, based on our simulations, that bias can be detected even if there is no bias in the current trial's strike pattern under certain conditions: if there are a sufficient number of historical cases (e.g., n=3) and if bias in the historical trials is sufficiently strong (i.e., strong incompatibilty). Contrary to this comment, this is exactly why we advocate for the use of $\alpha$! In scenarios like the one just described (n=3, strong incompatibility), sensitivity of bias detection can be evaluated by changing alpha and noting its effect on the estimation of bias.

@@

We have revised this discussion to remove such confusion.  The choice of the credible interval is a decision about how conservative one wishes to be about inferring bias from past strike data alone. We define bias "detection" narrowly to mean when $b = 0$ falls outside the chosen credible interval. Thus, the larger the credible interval, the greater the chance that zero falls within it. For the sake of clarity, we now focus on one credible interval (95%) in the paper and have placed simulation results based on other credible intervals in the Appendix. This does not necessarily fix the type I error, because this coverage probability refers to the true bias parameter (that is fixed in our simulations), and we are interested in "bias detection", i.e. whether the credible interval includes 0 or not. We also present sensitivity analysis for the selection of the nominal credible interval level.

@@

>2. About the results presented in Figure 1 of Section 2.3, if we **ignore the assumption of compatibility** between historical and current data, in the cases of $\alpha$ = 0.5 and $\alpha$ = 1, does the bottom right corner in each panel indicate that the bias detection rate can be as high as 100% even when the true current bias is 0? If so, the Type I error seems to be very high in some cases. Similarly, the power (bias detection rate) seems low at the top left corner in each panel where bias is low in historical data but high in current data.

@@

[Maybe mention that these issues - low power, type I error, etc are not unique to our method?]

@@

[INSERT] Will get Eric to check this (got a response from Xiaomeng - waiting for follow-up)

@@

[Mention that measuring incomaptibility and choice of a $\alpha$ in face of incompatibility is an active area of research (refs) with no clear solution. Our providing range of alpha values so that users can evaluate sensitivity is common practice (carvallo & ibrahim 2021)]
